\documentclass[letterpaper]{article}
\usepackage{natbib,alifeconf}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{url}

\title{Searching for an Eighth Criterion of Life:\\
A Falsifiable Framework and Two Null Results}

\author{Anonymous}

\begin{document}
\maketitle

\begin{abstract}
The textbook seven criteria of life---cellular organization, metabolism,
homeostasis, growth, reproduction, response to stimuli, and
evolution---are widely used to characterize living systems, yet it
remains unclear whether they suffice to explain resilience under novel
perturbations.  We present a falsifiable framework for evaluating
candidate eighth criteria, grounded in functional analogy: each
criterion must be a dynamic, energy-consuming process whose ablation
causes measurable degradation and whose activity forms feedback loops
with other criteria.  We extend this framework with an additional
requirement for candidate eighth criteria---experience-dependence or
collective signal utilization---and define three legitimacy tests:
orthogonality, non-reducibility, and causal necessity.  Using a hybrid
swarm-organism simulator implementing all seven criteria as
interdependent, ablatable processes, we test two candidates under
famine and boom-bust perturbation regimes ($n=30$ seeds per condition,
held-out test set): \textbf{Candidate~A} (within-lifetime
learning via EMA-driven homeostatic correction) and \textbf{Candidate~B}
(collective organization via kin-sensing).  Both yield null results: all
adjusted $p$-values $\geq 0.33$ (Holm--Bonferroni), all $|d| < 0.42$
(Cohen's~$d$), below our pre-specified smallest effect size of interest
($d = 0.5$).  Crucially, the nulls are \emph{diagnosed}: Candidate~A's
memory mechanism converges correctly (EMA late variance $p < 10^{-9}$
vs.\ sham) but provides no survival advantage; Candidate~B's kin signal
becomes degenerate (mean \texttt{kin\_fraction} 0.03 under famine, 0.19
under boom-bust---driven by rare multi-agent survivors) as organisms
converge to single-agent configurations under population caps.  These
bounded null results constrain the observed effect size of each candidate
below practical significance in the tested regimes, while the validated
protocol and diagnostic methodology provide a reusable template for
future candidate evaluation.
\end{abstract}

%% ================================================================
\section{Introduction}

What makes a system life-like?  Introductory biology textbooks
commonly enumerate seven criteria: cellular organization, metabolism,
homeostasis, growth and development, reproduction, response to stimuli,
and evolution \citep{urry_2020_campbell}.  These criteria serve as a
practical checklist, yet whether they constitute a \emph{sufficient}
characterization of life---especially under novel or extreme
conditions---remains an open question
\citep{cleland_2002_defining, benner_2010_defining}.

Artificial life research has long sought to operationalize these
criteria computationally.  Systems such as Tierra \citep{ray_1991_approach},
Avida \citep{ofria_2004_avida}, Polyworld \citep{yaeger_1994_computational},
Lenia \citep{chan_2019_lenia}, and ALIEN \citep{heinemann_2008_alien}
each implement subsets of life-like properties, from self-replication and
open-ended evolution to continuous morphogenesis.  Recent work on
Flow-Lenia \citep{plantec_2023_flow} and Coralai
\citep{barbieux_2024_coralai} pushes toward mass-conserving,
embodied neural ecosystems.  Theoretical frameworks from autopoiesis
\citep{maturana_1980_autopoiesis} through chemoton theory
\citep{ganti_2003_principles} emphasize the integration of metabolic,
boundary, and informational subsystems as minimal requirements
\citep{ruizmirazo_2004_universal}.

Despite this rich landscape, few systems implement \emph{all seven}
criteria as interdependent, individually ablatable processes---and
fewer still ask whether the seven are \emph{sufficient}.
\citet{bedau_2000_open} identified open problems in ALife that implicitly
point beyond the seven, including the evolution of adaptive behavior
and the emergence of collective organization.
The question we address is methodological: \emph{how should one
rigorously test whether an additional criterion provides explanatory
power beyond the existing seven?}

We contribute:
\begin{enumerate}
\item A \textbf{falsifiable evaluation protocol} for candidate eighth
  criteria, extending the functional analogy framework with three
  legitimacy tests (orthogonality, non-reducibility, causal necessity)
  and equivalence-based statistical framing.
\item \textbf{Rigorous null results} for two candidates---within-lifetime
  learning/memory and collective kin-sensing---each tested under two
  perturbation regimes with $n=30$ seeds, four conditions (baseline,
  candidate enabled, ablated, sham control), and Holm--Bonferroni
  correction.
\item \textbf{Mechanistic diagnoses} explaining each null: the memory
  mechanism works but adds no survival advantage; the kin signal becomes
  degenerate under the tested demographic regime.
\end{enumerate}

Reporting null results is essential for cumulative science
\citep{rosenthal_1979_file, fanelli_2012_negative}.  By defining our
smallest effect size of interest (SESOI) \emph{a priori} and bounding
all observed effects below it, we transform ``failure to reject $H_0$''
into a bounded null result
\citep{lakens_2017_equivalence, lakens_2018_sesoi}: the effect of each
candidate, if any, is smaller than a medium effect size under the tested
regimes.


%% ================================================================
\section{Methods}

\subsection{System Architecture}

Our simulator implements a hybrid two-layer architecture.  At the lower
level, \textbf{swarm agents} (10--50 per organism) inhabit a continuous
2D environment and maintain organism cohesion through local coordination.
At the upper level, \textbf{organisms} (10--50 per simulation) emerge
from coordinated agent groups and possess individual genomes, neural
controllers, and metabolic state.

Each of the seven biological criteria is realized as a \emph{functional
analogy}: a computational process that (a)~is a dynamic process
requiring sustained resource consumption, (b)~whose removal causes
measurable degradation of organism self-maintenance, and (c)~forms
feedback loops with at least one other criterion.  The seven criteria
map to specific subsystems:
\begin{enumerate}
\item \textbf{Cellular organization}: Active boundary maintenance via
  swarm coordination; degrades without energy.
\item \textbf{Metabolism}: Graph-based multi-step transformation
  network converting environmental resources to internal energy.
\item \textbf{Homeostasis}: Neural network controller regulates an
  internal state vector within viable ranges.
\item \textbf{Growth/Development}: Minimal seed state develops into
  mature organism via genetically encoded developmental program.
\item \textbf{Reproduction}: Organism-initiated division when
  metabolically ready; offspring develop from seed.
\item \textbf{Response to stimuli}: Local sensory field processed by
  neural network; emergent behavioral repertoire.
\item \textbf{Evolution}: Heritable genomes with mutation and
  recombination; differential survival drives adaptation.
\end{enumerate}

All organisms share a fixed-topology neural controller
($8 \to 16 \to 4$, 212 weights) with genome-encoded weights evolved
through tournament selection.  Simulations run for 10{,}000 timesteps
with deterministic seeding (same seed $+$ config $\to$ identical
output).


\subsection{Extending to an Eighth Criterion}

To avoid the ``arbitrary add-on'' criticism, we require any candidate
eighth criterion to satisfy the same functional analogy conditions
(a)--(c) plus an additional condition specific to the candidate's
domain.  We further define three \textbf{legitimacy tests}:

\begin{enumerate}
\item \textbf{Orthogonality}: The candidate must explain outcome
  variance \emph{after controlling for} signals from the existing seven
  criteria.
\item \textbf{Non-reducibility}: The baseline (seven criteria only)
  cannot match the candidate's effect by retuning existing parameters.
\item \textbf{Causal necessity}: Ablating the candidate causes
  measurable degradation under appropriate conditions.
\end{enumerate}

A candidate that fails any legitimacy test under a given regime receives
a \emph{regime-specific null}, not a universal rejection---the
candidate may succeed under different ecological conditions.

In this study, we focus on \textbf{causal necessity} (ablation testing)
as the primary empirical test, supplemented by mechanism verification.
Orthogonality and non-reducibility analyses remain important for
future work with positive-result candidates (see Limitations).


\subsection{Experimental Design}

For each candidate $\times$ perturbation regime, we run four conditions
on $n = 30$ held-out seeds (seeds 100--129, disjoint from the
calibration set 0--99):
\begin{enumerate}
\item \textbf{Baseline}: Seven criteria active, candidate inactive.
\item \textbf{Candidate enabled}: Candidate mechanism active.
\item \textbf{Candidate ablated}: Candidate mechanism zeroed/disabled,
  everything else identical to the enabled condition.
\item \textbf{Sham control}: Compute-matched random updates replacing
  the candidate's actual mechanism.
\end{enumerate}

Two perturbation regimes stress the system beyond normal operating
conditions:
\begin{itemize}
\item \textbf{Famine}: Resource availability drops to near-zero at
  step~3{,}000, creating acute survival pressure.
\item \textbf{Boom-bust}: Cyclic resource availability with period
  2{,}500 steps, creating recurring bottlenecks.
\end{itemize}

\paragraph{Statistical pipeline.}
Primary outcomes are survival AUC (total organism-steps) and
post-shock AUC (organism-steps after perturbation onset).  Pairwise
comparisons use Mann--Whitney $U$ tests \citep{mann_1947_test} with
Holm--Bonferroni correction \citep{holm_1979_simple} for multiple
comparisons.  Effect sizes are reported as Cohen's~$d$
\citep{cohen_1988_statistical}.

\paragraph{Equivalence framing.}
We pre-specify a smallest effect size of interest (SESOI) of $d \geq
0.5$ (medium effect per Cohen's conventions).  With $n = 30$ per
condition, we have approximately 80\% power to detect $d \geq 0.5$.
If all observed $|d| < 0.5$ and adjusted $p$-values remain
non-significant, we interpret this as a bounded null: the candidate's
effect, if any, is smaller than a medium effect size in the tested
regime.  We note that formal equivalence testing (e.g., TOST;
\citealt{lakens_2017_equivalence}) would further strengthen this claim
but is beyond the scope of the current analysis.


%% ================================================================
\section{Candidate A: Within-Lifetime Memory}

\subsection{Implementation}

Candidate~A adds a \textbf{memory-driven homeostatic correction phase}
operating alongside (but separately from) the neural controller.  Each
organism maintains a 2-element exponential moving average (EMA) tracking
the mean internal state of its agents:
\begin{equation}
m_{t+1}^{(i)} = \alpha \cdot m_t^{(i)} + (1 - \alpha) \cdot
\bar{s}_t^{(i)}, \quad i \in \{0, 1\}
\end{equation}
where $\bar{s}_t^{(i)}$ is the mean of internal-state channel~$i$ across
the organism's agents, and $\alpha \in [0, 1]$ is a configurable decay
parameter.  The memory trace drives a proportional correction toward a
genome-modulated target: four genome-encoded parameters (two gains, two
targets) control the strength and set-point of the correction, which is
applied directly to agent internal states each timestep.  Memory is
initialized to zero at birth.  The neural controller architecture
(212~weights for the base 8-input topology) is unchanged; the memory
phase adds only four evolvable genome parameters.

This design satisfies the functional analogy conditions: it is a dynamic
process (continuous EMA updates consuming internal-state signals), its
ablation is clean (skip the correction phase), and it couples with
homeostasis (modifying internal state) and response-to-stimuli (internal
state feeds the neural controller).  The additional condition for
Candidate~A is \textbf{experience-dependence}: performance should improve
as a function of within-lifetime experience under stationary genetics.

The \textbf{sham control} replaces the EMA trace with independent uniform
random draws each timestep, preserving the correction code path and
computational cost while destroying temporal coherence
\citep{floreano_2000_evolutionary, soltoggio_2018_born}.

\subsection{Results}

Table~\ref{tab:results} summarizes outcomes across three experiment
suites.

\subsubsection*{Normal conditions (no perturbation)}
Survival AUC: $+106.5$ vs.\ baseline ($d = 0.13$, $p_\mathrm{adj} =
0.94$).  No significant effect.  Ablated and sham conditions are
similarly indistinguishable from baseline ($d < 0.10$).

\subsubsection*{Famine stress}
Post-shock AUC: $+7.3$ ($d = 0.03$, $p_\mathrm{adj} = 1.0$).  Baseline
extinction rate 86.7\%, enabled 93.3\%.  Memory provides no survival
advantage under acute resource deprivation.

\subsubsection*{Boom-bust stress}
Survival AUC: $-103.2$ ($d = -0.28$, $p_\mathrm{adj} = 0.46$).
Extinction: 93.3\% for both baseline and enabled, but only 70.0\% for
the ablated condition and 66.7\% for sham---a pattern suggesting that
disabling or randomizing the memory correction may reduce destabilizing
homeostatic interference under cyclic stress, though none of these
differences reach significance after correction.

\subsection{Mechanism Verification}

Despite the null survival effect, the memory mechanism itself operates
correctly.  The EMA late variance (variance of memory vectors across
the final 1{,}000 timesteps) is significantly lower for the enabled
condition ($\bar{\sigma}^2 = 1.04 \times 10^{-4}$) than for the sham
control ($\bar{\sigma}^2 = 7.29 \times 10^{-4}$; Mann--Whitney
$U = 33$, $p < 10^{-9}$).  This confirms that the EMA converges to a
stable representation of sensory experience---it simply does not
provide actionable information for survival under the tested regimes.

The distinction between ``mechanism works'' and ``mechanism helps'' is
critical: the memory faithfully encodes experience, but the
evolutionary landscape under these perturbation regimes does not select
for memory-contingent behaviors.


%% ================================================================
\section{Candidate B: Collective Kin-Sensing}

\subsection{Implementation}

Inspired by Hamilton's inclusive fitness theory
\citep{hamilton_1964_genetical, west_2007_social}, Candidate~B adds a
\textbf{kin-sensing channel} that provides each agent with information
about nearby relatives.  A single-pass neighbor count
(\texttt{count\_neighbors\_split}) partitions nearby agents into kin
(same genome lineage) and non-kin, computing a \texttt{kin\_fraction}
$\in [0, 1]$ that enters the neural controller as an additional input
(channel~8, expanding the input from 8 to 9 dimensions; 228 total
weights).

This satisfies the functional analogy: it is a dynamic process
(recomputed each timestep from local spatial information), its ablation
is clean (fix \texttt{kin\_fraction} = 0), and it couples with
cellular organization (spatial structure determines kin encounters) and
reproduction (kin density reflects reproductive success).  The
additional condition for Candidate~B is \textbf{collective signal
utilization}: organisms with access to kin information should exhibit
measurably different (and more resilient) collective behavior.

The \textbf{sham control} permutes real \texttt{kin\_fraction} values
across alive agents each timestep, preserving the population-level
distribution while destroying the spatial correlation between an
organism and its actual neighbors.

\subsection{Results}

Table~\ref{tab:results} shows Candidate~B results under both
perturbation regimes.

\subsubsection*{Famine stress}
Post-shock AUC: $-38.3$ vs.\ baseline ($d = -0.13$, $p_\mathrm{adj} =
1.0$).  Extinction: 96.7\% enabled vs.\ 86.7\% baseline.  All
conditions statistically equivalent.

\subsubsection*{Boom-bust stress}
Survival AUC: $-32.3$ ($d = -0.08$, $p_\mathrm{adj} = 1.0$).
Extinction: 76.7\% enabled vs.\ 83.3\% baseline.  Again, no significant
differences.

\subsection{Signal Sparsity Diagnosis}

The null result for Candidate~B has a clear mechanistic explanation:
\textbf{organisms converge to approximately one agent each} under the
population cap.  When organisms consist of a single agent, the
kin-sensing neighborhood is dominated by non-kin agents from other
single-agent organisms, yielding a \texttt{kin\_fraction} near zero.

Quantitatively, the mean \texttt{kin\_fraction} at simulation end is
0.03 under famine and 0.19 under boom-bust (with high variance driven
by rare multi-agent survivors).  In the pre-shock phase, organisms
maintain larger swarms ($\sim$90--100 agents), but the perturbation
collapses populations to single-agent organisms within a few hundred
steps.

This is an \emph{observability failure}: the kin signal exists in
principle but becomes degenerate under the tested demographic regime.
The null does not reject kin-sensing as a criterion \emph{in general},
but rather identifies a specific boundary condition---population caps
that force single-agent organisms---under which the signal cannot
provide information.


%% ================================================================
\section{Discussion}

\subsection{Interpreting Double-Null Results}

Both candidates yield null results across all tested regimes.  All
point estimates are small: the largest observed effect is $|d| = 0.41$
(Candidate~A, boom-bust, sham; 95\% CI $[-0.92, 0.10]$;
$p_\mathrm{adj} = 0.33$).  However, with $n = 30$ per condition, the
95\% confidence intervals for Cohen's~$d$ are wide (typical half-width
$\approx 0.51$), and no single comparison's CI falls entirely within
$[-0.5, 0.5]$.  Thus, while all point estimates lie below our SESOI,
the data cannot formally exclude medium effects---a power limitation
inherent to the sample size.  Formal equivalence testing (TOST) would
require either larger samples or pooling across regimes.

Importantly, these are \emph{diagnosed} nulls.  Each candidate fails
for a different reason:

\begin{itemize}
\item \textbf{Candidate~A} (Memory): The mechanism works---EMA converges
  correctly and encodes sensory history---but the evolutionary landscape
  does not select for memory-contingent behaviors under the tested
  perturbations.  The within-lifetime information the memory accumulates
  is not \emph{actionable} given the structure of the perturbation
  regimes (sudden onset with no recovery signal to learn from).
\item \textbf{Candidate~B} (Kin-Sensing): The mechanism is rendered
  non-functional by demographic convergence to single-agent organisms
  under population caps, making the kin signal degenerate before it can
  be utilized.  This is a regime-specific boundary condition, not a
  general failure of kin-based collective sensing.
\end{itemize}

\subsection{Implications for Multi-Scale ALife Design}

The diagnosed nulls reveal important design principles for ALife
systems aiming to test collective or experiential criteria:

\textbf{Signal viability precedes signal utility.}  Candidate~B
demonstrates that a theoretically well-motivated mechanism can fail not
because of its logic but because ecological dynamics eliminate the
conditions under which the signal carries information.  Future systems
testing collective organization must ensure that multi-agent organisms
persist at sufficient scale for inter-organism signals to be
meaningful.

\textbf{Perturbation structure matters for learning.}  Candidate~A's
memory accumulates information, but the famine regime offers no
within-lifetime gradient to learn from---it is a single catastrophic
event.  Future tests of learning/memory should include perturbation
regimes with \emph{repeated, learnable structure} (e.g., predictable
seasonal cycles where past experience is informative about future
conditions).

\textbf{Mechanism verification is essential.}  Without the EMA
convergence test (Candidate~A) and kin-fraction analysis
(Candidate~B), the null results would be uninterpretable---they could
indicate either ``the mechanism doesn't help'' or ``the mechanism
doesn't work.''  Separating these cases is critical for cumulative
progress.


\subsection{Limitations}

Several limitations constrain the generalizability of our findings.

\textbf{Regime specificity.}  Our two perturbation regimes (famine,
boom-bust) represent acute environmental stress.  Candidates may succeed
under gradual perturbations, repeated exposure regimes, or spatial
heterogeneity---conditions we did not test.

\textbf{Population caps.}  The population cap
($\texttt{max\_alive\_organisms} = 100$) creates a demographic ceiling
that drives convergence to minimal-size organisms.  This is a design
constraint (compute budget on M2 Pro hardware), not a theoretical
necessity.  Relaxing this constraint could restore the viability of
kin-based signals.

\textbf{Controller capacity.}  The fixed-topology neural controller
($8/9 \to 16 \to 4$) may lack the representational capacity to exploit
memory or kin information.  Larger or more flexible controllers (e.g.,
NEAT-style topology evolution; \citealt{stanley_2002_evolving}) could
change the outcome.

\textbf{Two candidates, one system.}  We test two candidates in one
simulator.  Different substrate architectures (e.g., continuous CA,
voxel-based robots) may support different candidate mechanisms more
naturally.

\textbf{Legitimacy test scope.}  Of the three proposed legitimacy tests,
we empirically evaluated only causal necessity (ablation) and mechanism
verification.  Orthogonality and non-reducibility analyses---which
require fitting predictive models and running retuned baselines---are
most informative for positive-result candidates and remain as future
work.


\subsection{What Would Count as Success}

To guide future work, we pre-specify criteria that a successful
candidate eighth criterion must meet:

\begin{enumerate}
\item \textbf{Effect size}: Cohen's $d \geq 0.5$ on survival AUC for
  enabled vs.\ baseline, sustained across $\geq 2$ perturbation regimes.
\item \textbf{Ablation}: Significant degradation ($p_\mathrm{adj}
  < 0.05$) when the candidate is ablated relative to the enabled
  condition.
\item \textbf{Sham inequality}: Enabled condition significantly
  outperforms the sham control, ruling out compute confounds.
\item \textbf{Mechanism verification}: Quantitative evidence that the
  candidate mechanism operates as designed (analogous to our EMA
  convergence test).
\end{enumerate}


%% ================================================================
\section{Conclusion}

We presented a falsifiable framework for evaluating candidate eighth
criteria of life-likeness, grounded in functional analogy, ablation
controls, sham comparisons, and equivalence-based statistical analysis.
Applying this framework to two candidates---within-lifetime memory
(Candidate~A) and collective kin-sensing (Candidate~B)---across two
perturbation regimes with $n = 30$ seeds each, we obtain bounded null
results: all effects are below our pre-specified SESOI of $d = 0.5$.

The contribution is threefold.  First, the evaluation protocol itself is
reusable and extensible to future candidates---it defines what would
count as evidence for or against any proposed criterion.  Second, the
diagnosed nulls constrain the design space: future candidates targeting
within-lifetime adaptation should ensure perturbation regimes with
learnable temporal structure, and candidates targeting collective
organization should ensure multi-agent organisms persist at viable
scale.  Third, by reporting these null results explicitly, we contribute
to the cumulative record of what has been tested and ruled out under
specific conditions.

The search for what, if anything, lies beyond the textbook seven criteria
remains open.  Our framework provides a systematic, falsifiable approach
to that search.


%% ================================================================

% Results table
\begin{table*}[t]
\centering
\caption{Summary of results across all experiment suites.  $\Delta$AUC
is the difference in mean AUC (enabled $-$ baseline).  $d$ is Cohen's
$d$.  $p_\mathrm{adj}$ is the Holm--Bonferroni adjusted $p$-value.
Ext.\ is extinction rate.  All $|d| < 0.5$ (our SESOI).}
\label{tab:results}
\small
\begin{tabular}{@{}llrrrrl@{}}
\toprule
\textbf{Candidate} & \textbf{Regime} & \textbf{Metric} &
\textbf{$\Delta$AUC} & \textbf{$d$} & \textbf{$p_\mathrm{adj}$} &
\textbf{Ext.\ (\%)} \\
\midrule
\multicolumn{7}{@{}l}{\textit{Candidate A: Memory}} \\
\quad Enabled & Normal & Surv.\ AUC & $+106.5$ & $0.13$ & $0.94$ & --- \\
\quad Ablated & Normal & Surv.\ AUC & $+80.7$ & $0.10$ & $0.94$ & --- \\
\quad Sham    & Normal & Surv.\ AUC & $+76.6$ & $0.09$ & $0.94$ & --- \\
\addlinespace
\quad Enabled & Famine & Post-shock & $+7.3$ & $0.03$ & $1.00$ & 93.3 \\
\quad Ablated & Famine & Post-shock & $+19.9$ & $0.08$ & $1.00$ & 76.7 \\
\quad Sham    & Famine & Post-shock & $+46.0$ & $0.18$ & $1.00$ & 80.0 \\
\addlinespace
\quad Enabled & Boom-bust & Surv.\ AUC & $-103.2$ & $-0.28$ & $0.46$ & 93.3 \\
\quad Ablated & Boom-bust & Surv.\ AUC & $-120.2$ & $-0.31$ & $0.46$ & 70.0 \\
\quad Sham    & Boom-bust & Surv.\ AUC & $-167.8$ & $-0.41$ & $0.33$ & 66.7 \\
\midrule
\multicolumn{7}{@{}l}{\textit{Candidate B: Kin-Sensing}} \\
\quad Enabled & Famine & Post-shock & $-38.3$ & $-0.13$ & $1.00$ & 96.7 \\
\quad Ablated & Famine & Post-shock & $-49.8$ & $-0.16$ & $1.00$ & 86.7 \\
\quad Sham    & Famine & Post-shock & $+31.7$ & $0.11$ & $1.00$ & 80.0 \\
\addlinespace
\quad Enabled & Boom-bust & Surv.\ AUC & $-32.3$ & $-0.08$ & $1.00$ & 76.7 \\
\quad Ablated & Boom-bust & Surv.\ AUC & $+100.9$ & $0.28$ & $0.75$ & 86.7 \\
\quad Sham    & Boom-bust & Surv.\ AUC & $+44.2$ & $0.11$ & $1.00$ & 80.0 \\
\bottomrule
\end{tabular}
\end{table*}


\footnotesize
\bibliographystyle{apalike}
\bibliography{references}

\end{document}
